Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-09-06 manuscript/climate_sensitivity_draft.Rmd
TLP significance
#134

- Individual-level drought resistance decreased with tree height, which was strongly correlated with exposure to higher evaporative demand and solar radiation. The potentially greater rooting volume of larger trees did not confer an advantage in sites with low topographic wetness index. Resistance was greater among species whose leaves experienced less shrinkage upon desiccation and lost turgor (wilted) at more negative water potentials.

>>>>

- Individual-level drought resistance decreased with tree height, which was strongly correlated with exposure to higher evaporative demand and solar radiation. The potentially greater rooting volume of larger trees did not confer an advantage in sites with low topographic wetness index. Resistance was greater among species whose leaves experienced less shrinkage upon desiccation and*, marginally, those whose leaves* lost turgor (wilted) at more negative water potentials.
